Self-reported LLM usage and outcomes on a data science project: Evidence from two undergraduate data science courses

### 2025-04-12 paper/paper.qmd
Very minor typo in the last sentence

Despite these shortcomings, our work clearly identifies a need for further research examining how LLMs can be used to develop a more trustworthy data science workflow, both in and outside of the classroom.

>>>>

Despite these shortcomings, our work clearly identifies a need for further research examining how LLMs can be used to develop a more trustworthy data science workflow, both in and out of the classroom.
